We present a lightweight, training-free Text-to-SQL pipeline that achieves
competitive execution accuracy on Spider~1.0 (\mbox{EX\,=\,0.824}) using a
9-billion-parameter local language model (Qwen3.5) paired with an
INT8-quantized arctic-embed-m schema retriever.
The pipeline requires no fine-tuning, no cloud API access, and runs entirely
on consumer hardware.

The core contribution is a systematic quantization study of the retrieval
encoder.
Dynamic INT8 quantization reduces retriever RAM by 78.2\% (418\,MB
$\to$ 91\,MB) and improves encoding latency by 15.2\% (64\,ms
$\to$ 54\,ms per query) with \textbf{zero retrieval-quality degradation}
($\Delta$R@5\,=\,0.0000, $\Delta$MRR\,=\,0.0000).
A per-block sensitivity analysis across all 12 transformer layers confirms
that uniform INT8 quantization is the globally optimal configuration.

The pipeline further incorporates five synergistic components---schema
retrieval, sql2skeleton few-shot selection, self-consistency candidate
generation (SC\,=\,3), and two-pass SQL correction---each evaluated in a
rigorous ablation study on 1{,}034 Spider~1.0 development questions
(all improvements $p < 0.001$, McNemar's test).
Validation on Spider~2.0-Lite demonstrates generalization to a
substantially harder benchmark, where the full pipeline achieves
EX\,=\,0.111 (up from 0.067 zero-shot baseline; few-shot retrieval
alone accounts for $+$55\% relative gain).

These results demonstrate that an edge-deployable Text-to-SQL system
with a quantized retrieval encoder introduces no measurable accuracy
penalty relative to its full-precision counterpart.
